%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Aman Ranjan} 
        \\ \vspace{1pt}
    \small +91 85916 46417 $|$ 
    \href{mailto:ranjanaman0711@gmail.com}
        {\underline{ranjanaman0711@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/aman-ranjan-b6662328a/}
        {LinkedIn} $|$
    \href{https://github.com/ikuchbhi}
        {GitHub}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {BITS Pilani, Hyderabad Campus}{Hyderabad, India}
      {B.E. (Hons.) in Computer Science - CGPA 8.46/10.0}{Oct. 2022 - May 2026}
    \resumeSubheading
      {New Bombay City School}{Navi Mumbai, India}
      {12th Grade - CBSE - 92.6\%}{Apr. 2021 - Mar. 2022}
    \resumeSubheading
      {ASP Public School}{Navi Mumbai, India}
      {10th Grade - CBSE - 97.4\%}{Apr. 2019 - Mar. 2020}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item{
            \textbf
            {Languages}
            {: Java, Python, C, C++, SQL (Postgres), JavaScript, HTML/CSS, ReactJS, Dart} \\
            \textbf
            {Frameworks}
            {: ReactJS, NodeJS, Flutter, ExpressJS, NodeJS} \\
            \textbf
            {Developer Tools}
            {: Git, Docker, GitHub Actions}
        }
    }
 \end{itemize}
%-------------------------------------------

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Summer Intern}{May 2024 - Jul. 2024}
      {Contenterra Software Pvt. Ltd.}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{Flutter-based Personal Search Assistant (PSA) application} to access data from various sources such as Google Drive, DropBox and Evernote}
        \resumeItem{Implemented \textbf{unit tests} and \textbf{Github Actions} to automate running tests and building the application, reducing redundant development cycles by \textbf{50\%}}
      \resumeItemListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {
            \textbf{FestMate} $|$ 
            \emph{Python, FastAPI, ReactJS, PostgreSQL, Docker} \\
        }{}
        \resumeItemListStart
            \resumeItem{Engineered a full-stack web-based fest management platform with a \textbf{FastAPI backend} and \textbf{ReactJS frontend}, capable of handling event registrations for \textbf{1000+ users in real-time.}}
            \resumeItem{Optimized database performance by implementing \textbf{PostgreSQL triggers and indexes}, reducing data retrieval times by 30\%, ensuring efficient large-scale data operations.}
            \resumeItem{Leveraged Docker to containerize both frontend and backend, streamlining deployment and \textbf{reducing setup time by 50\%.}}
        \resumeItemListEnd
        
        \resumeProjectHeading
            {
                \textbf{KanbanDone} $|$ 
                \emph{NestJS, NodeJS, Docker, Flutter} \\
            }{}
        \resumeItemListStart
            \resumeItem{A Trello-like application that organizes Tasks into Lists and Boards to enhance productivity for projects}
            \resumeItem{Implemented the backend using \textbf{NestJS} and containerized it using \textbf{Docker}; the frontend is written in \textbf{Flutter.}}
            \resumeItem{Implemented Card drag-and-drop functionality and realtime synchronization via \textbf{Socket.io} to enhance productivity.}
        \resumeItemListEnd
    
    \resumeProjectHeading
        {
            \textbf{BITSBids} $|$ 
            \emph{ReactJS, NodeJS, Docker, Spring Boot} \\
        }{}
        \resumeItemListStart
            \resumeItem{Developed an auction-based marketplace for \textbf{300+ BITSians} to buy and sell used goods, featuring a \textbf{real-time bidding system with secure transactions.}}
            \resumeItem{Implemented real-time chat functionality using \textbf{Socket.io}, facilitating instant communication between buyers and sellers.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Positions of Responsibility}
    \resumeProjectHeading
        {
            \textbf{Technical Team Lead, SWD Nucleus}
        }{}
        \resumeItemListStart
            \resumeItem{Developed a payment gateway for various outlets on campus, catering to \textbf{5000+ students} and handling \textbf{1000+ orders per day} overall}
            \resumeItem{Implemented a outstation portal for smart entry-exit into the campus, reducing wait times and redundancies by 75\%}
            \resumeItem{Built the \textbf{SWD BPHC} app, used by \textbf{3000+ students regularly} to access various student-related services}
            \resumeItem{Conducted monthly mess registrations for 5000+ students on campus}
        \resumeItemListEnd
\end{document}
